\documentclass[../DC2019003Bouma.tex]{subfiles}
\begin{document}
\cleartooddpage
\chapter*{Acknowledgments}\phantomsection\addcontentsline{toc}{chapter}{Acknowledgments}
With the final words of my thesis on paper, I can happily say that I look back on an exciting year. Exploring the many fields that my thesis is involved with has been a great experience, and this is mainly due to the people I got to share it with. I would like to take this opportunity to thank these people, for their impact on the work that lies before you.

First of all, I want to express my gratitude to my supervisors. Our collaboration was one of the main things that made writing this thesis so enjoyable to me. Nathan, your feedback and critical look were very beneficial to my work. Especially our discussions on nonsmooth mechanics have often completely changed my understanding of the subject. I am thankful for all that I have learned from you. Alessandro, before I talked to you about the subject of my Master's thesis, I would have never imagined myself going for such a highly theoretical subject. Your enthusiasm about your work is what made me decide otherwise. During my project, I could always count on honest and critical feedback on your part, which has greatly influenced my work for the better. And Mark, many times have I knocked on the door of your office, and you would always give me the minute that I asked for. Even when you had your own deadlines to worry about, you took the time to help me get back on track if I was lost. Your continuous input has significantly improved the result of this thesis.

I also want to thank my fellow students of the robotics lab. I could not have asked for a better environment to write my thesis in. Being able to share my struggles with you has made it that much easier to stay motivated throughout my project. The insightful discussions we had while enjoying our oerknack, scoopies and knakkies were always a highlight of my day. I especially want to thank Casper, for facing the giant called reference spreading together with me.

I am also grateful for my friends, brother and sister, The Elephants, Carbo, and de Raad der Stokken. It was nice to have you as welcome distractions from my work. This work would have not been possible without your friendship and support. Special thanks go towards Charlotte, you have always sparked my ambition and motivated me to give this my best. I truly appreciate the great times we have spent together, and your support in the bad. Thank you.

Finally, I want to sincerely thank my parents, Jasper and Hiltje. My time as a student has brought me great experiences, and a large part of this I owe to you. Your support has allowed me to chase opportunities that otherwise would not have been possible. Whatever my next step is in life, I know you will be in my corner, like you have been in the past. For this, I am truly grateful.\\\\\\\\
Menno Bouma\\
\textit{January 2019, Eindhoven}
\end{document}